cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Add intro paragraph for branching

The

Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.

>>>>

A branching structure captures trajectories that diverge or bifurcate from a common origin, resembling processes such as cell differentiation in biology. We introduce a set of data generation functions specifically designed to simulate high-dimensional branching structures with various geometry, number of points, and the number of branches. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:branching-tb-html)', '\\@ref(tab:branching-tb-pdf)'))` outlines these functions. The main arguments of the functions described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:arg-branching-tb-html)', '\\@ref(tab:arg-branching-tb-pdf)'))`.
